Assignment 1
========================================================


```{r}

```


### Task 1 - Dealing with a numeric vector [3 points in total]


Consider the following numeric vector.

```{r}
x <- c(34, 56, 55, 87, NA, 4, 77, NA, 21, NA, 39)
```

a)  What's the mean of all values? [1 point]

```{r}
mean(x,na.rm = T)
```

b) And what's the median? What about the variance and the standard deviation? [1 point]

```{r}
median(x,na.rm = T)
var <- var(x,na.rm = T)
SD <- sqrt(var)
```

c) Compute the sum of all values. [1 point]

```{r}
sum(x,na.rm = T)
```

<br>

========================================================

### Task 2 - Dealing with a character vector  [4 points in total]

Consider the following character vector.

```{r}
friends <- c("Homer", "Marge", "Bart", "Lisa", "Maggie")
```


a) Get the length of the vector. [1 point]

```{r}
length(friends)
```

b) Extract the first two friends of the vector. [1 point]

```{r}
friends[c(1:2)]
```

c) Extract the second and the last observation from the vector. [1 point]

```{r}
friends[c(2,5)]
```

d) Sort your friends by their names in reverse alphabetic order. [1 point]

```{r}
sort(friends,decreasing = T)
```


<br>

========================================================

### Task 3 - A dataset on immigration trips to Ellis Island  [4 points in total]

a) Load the dataset `immigration-ellis.tsv` into R, which contains data on immigration to Ellis Island (1918-1922) by trip. [1 point]

```{r}
immigration.ellis <- read.delim("C:/Users/user/Desktop/R lab/Stat-II/W1-Installing Gtub and Rmarck/LAB- ii/immigration-ellis.tsv")
```

b) What is the total number of immigration cases in the dataset? [1 point]

```{r}
length(immigration.ellis$Count)
```

c) From where did the ship with the most immigrants arrive? [1 point]

```{r}

```

d) How many unique ships (according to the name) are in the dataset? [1 point]

```{r}
length(unique(immigration.ellis$Ship))
```

e) Find out the name of the package from the tidyverse that makes working with date and times data easier, and report it below! [1 point]

<div style="color:blue">
lubridate' package
</div>





